Manuscript Title:\\with Forced Linebreak

### 2020-04-17 paper1.tex
recent works

\begin{equation}
{\cal L} = D - W
\end{equation}

@@

@@

\begin{equation}
Q^w = \frac{1}{I^w} \sum \limits_{i,j} \left[W_{ij} - \frac{k_i^w k_j^w}{I^w} \right] \delta(m_i, m_j),
\end{equation}

@@

@@

Voltage distribution at a specific time $t$ in the network can be roughly determined by the weighted current flow betweenness centrality. As shown in fig. \ref{fig:v_lam_cent}, voltage and filament state as functions of centrality is plotted.

@@

The transfer entropy across an edge ($e_{i,j}$) is calculated by:

\textbf{Have to write these equations in a better manner.}

@@

\subsection{Dual task}

@@

\bibliography{paper1} \label{paper1}% Produces the bibliography via BibTeX.
\bibliographystyle{apalike}

>>>>

\begin{equation}
{\cal L} = D - W.
\end{equation}

Here $W$ is the weighted adjacency matrix of the network. The weights on edges are determined based on their conductance:
\begin{equation}
	W_{ij} = A_{ij}G(i,j).
\end{equation}

And $D$ is the weighted degree matrix generated from $W$:
\begin{align}
	d_i = \sum \limits_{k=1}^{N} W_{i,k},\\
	D = \textbf{diag}(d_i).
\end{align}

@@

% \begin{equation}
% Q^w = \frac{1}{I^w} \sum \limits_{i,j} \left[W_{ij} - \frac{k_i^w k_j^w}{I^w} \right] \delta(m_i, m_j),
% \end{equation}
\begin{equation}
Q^w = \frac{1}{D} \sum \limits_{i,j} \left[W_{ij} - \frac{d_i d_j}{D} \right] \delta(m_i, m_j),
\end{equation}

@@

The transfer entropy across an edge ($e_{i,j}$) is calculated by:
\textbf{Have to write these equations in a better manner.}

@@

As the network evolves, the edges close to sources and drains will be turned on first. A winner-takes-all current path will form, then branches out to the rest of the network. Among all sorts of metrics, voltage distribution on nodes $\vec{V_n}$ and on edges $\vec{V_e}$ would be the most important ones as they determine the network's state.

@@

Voltage distribution on edges at a specific time $\vec{V_e}(t)$ shows a clear correlation with edge current flow betweenness centrality. Meanwhile, since the filament states $\lambda$ strongly rely on voltage distribution $\vec{V_e}(t)$, a correlation between $\lambda$ and EBC as well. As plotted in fig. \ref{fig:v_lam_cent}, for $\vec{V_e(t)}$ two linear groups

@@

@@

\subsection{Dual task}
\textbf{Might change to a smaller amplitude. Here modularity peak at $t=10$, too small to capture TE.}

@@

\bibliography{paper1} \label{paper1}% Produces the bibliography via BibTeX.
